\large\bfseries Soliton Solution, B\"acklund Transformation, Conservation Laws, and rogue wave solution for a generalized variable-coefficient Sasa-Satsuma-like equation

### 2018-05-07 me/modify2/paper/paper.tex
update

\small
\bibliographystyle{unsrt}
\bibliography{ref}

\end{document}

>>>>

\begin{thebibliography}{15}
\bibitem{1}
Zhang, Yu-Ping and Yu, Lan and Wei, Guang-Mei. Integrable aspects and rogue wave solution of Sasa--Satsuma equation with variable coefficients in the inhomogeneous fiber. Modern Physics Letters B, 32(05):1850059, 2018.

\bibitem{2}
Chen, Shihua. Twisted rogue-wave pairs in the Sasa-Satsuma equation. Physical Review E, 88(2):023202,2013.

\bibitem{3}
Mu, Gui and Qin, Zhenyun. Dynamic patterns of high-order rogue waves for Sasa--Satsuma equation. Nonlinear Analysis: Real World Applications, 31:179--209,2016.

\bibitem{4}
Soto-Crespo, JM and Devine, Natasha and Hoffmann, NP and Akhmediev, Nail. Rogue waves of the Sasa-Satsuma equation in a chaotic wave field. Physical Review E,90(3):032902,2014.

\bibitem{5}
Xu, Tao and Li, Min and Li, Lu. Anti-dark and Mexican-hat solitons in the Sasa-Satsuma equation on the continuous wave background. EPL (Europhysics Letters),109(3):30006,2015.

\bibitem{6}
Liu, Lei and Tian, Bo and Chai, Han-Peng and Yuan, Yu-Qiang. Certain bright soliton interactions of the Sasa-Satsuma equation in a monomode optical fiber. Physical Review E,95(3):032202,2017.

\bibitem{7}
Liu, Ying and Gao, Yi-Tian and Xu, Tao and L{\"u}, Xing and Sun, Zhi-Yuan and Meng, Xiang-Hua and Yu, Xin and Gai, Xiao-Ling. Soliton solution, B{\"a}cklund transformation, and conservation laws for the Sasa-Satsuma equation in the optical fiber communications. Zeitschrift f{\"u}r Naturforschung A,65(4):291--300,2010.

\bibitem{8}
Du, Zhong and Tian, Bo and Wu, Xiao-Yu and Liu, Lei and Sun, Yan. Conservation laws and rogue waves for a higher-order nonlinear Schr{\"o}dinger equation with variable coefficients in the inhomogeneous fiber. Superlattices and Microstructures,107:310--319,2017.

\bibitem{9}
Li, Min and Xu, Tao and Wang, Lei and Qi, Feng-Hua. Nonautonomous solitons and interactions for a variable-coefficient resonant nonlinear Schr{\"o}dinger equation. Applied Mathematics Letters,60:8--13,2016.

\bibitem{10}
Yuping, Zhang and Junyi, Wang and Guangmei, Wei and Ruiping, Liu. The Painlev{\'e} property, B{\"a}cklund transformation, Lax pair and new analytic solutions of a generalized variable-coefficient KdV equation from fluids and plasmas. Physica Scripta,90(6):065203,2015.

\bibitem{11}
Mahalingam, A and Alagesan, T. Singularity structure analysis of inhomogeneous Hirota and higher order nonlinear Schr{\"o}dinger equations. Chaos, Solitons \& Fractals,25(2):319--323,2005.

\bibitem{12}
Meng, Xiang-Hua and Liu, Wen-Jun and Zhu, Hong-Wu and Zhang, Chun-Yi and Tian, Bo. Multi-soliton solutions and a B{\"a}cklund transformation for a generalized variable-coefficient higher-order nonlinear Schr{\"o}dinger equation with symbolic computation. Physica A: Statistical Mechanics and its Applications,387(1):97--107,2008.

\bibitem{13}
Li, Zhonghao and Li, Lu and Tian, Huiping and Zhou, Guosheng. New types of solitary wave solutions for the higher order nonlinear Schr{\"o}dinger equation. Physical review letters,84(18):4096,2000.

\bibitem{14}
Yang, Rongcao and Li, Lu and Hao, Ruiyu and Li, Zhonghao and Zhou, Guosheng. Combined solitary wave solutions for the inhomogeneous higher-order nonlinear Schr{\"o}dinger equation. Physical Review E,71(3):036616,2005.

\bibitem{15}
Xu, Tao and Zhang, Chun-Yi and Wei, Guang-Mei and Li, Juan and Meng, Xiang-Hua and Tian, Bo. Symbolic-computation construction of transformations for a more generalized nonlinear Schr{\"o}dinger equation with applications in inhomogeneous plasmas, optical fibers, viscous fluids and Bose-Einstein condensates. The European Physical Journal B,55(3):323--332,2007.

\end{thebibliography}
\end{document}
